### 2017-07-26 paper/oopsla17-cameraready/evaluation.tex
add user study

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer three questions in our evaluation:
%
\begin{itemize}
\item \textbf{Blame Accuracy}
  %
  How often does \toolname
  blame a \emph{correct}
  location for the type error?
  (\autoref{sec:quantitative})
  %
  % We compare our technique with a variety of off-the-shelf classifiers
  % and find that our top-ranked blame assignments have an accuracy of
  % 72\%, compared to a state-of-the-art 56\%.
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item \textbf{Feature Utility}
  %
  Which program \emph{features are required}
  to localize errors?
   (\autoref{sec:feature-utility})
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item \textbf{Interpretability}
  %
  %% Do the models learned by \toolname
  %% correspond to our intuition about
  %% the real causes of errors?
  Are the models \emph{interpretable} using
  our intuition about type errors?
  (\autoref{sec:qualitative})
\end{itemize}
%
%\mypara{Summary of Results}
%
In the sequel we present our experimental
methodology \autoref{sec:methodology} and
then drill into how we evaluated each of
the questions above.
%
However, for the impatient reader, we begin
with a quick summary of our main results:
%
%
%\begin{itemize}
%
%\item \textbf

@@

\input{evaluation-accuracy}
\input{evaluation-utility}

>>>>

We have implemented our technique for localizing type errors for a
purely functional subset of \ocaml with polymorphic types and functions.
%
We seek to answer four questions in our evaluation:
%
\begin{itemize}
\item \textbf{Blame Accuracy}
  %
  How often does \toolname
  blame a \emph{correct}
  location for the type error?
  (\autoref{sec:quantitative})
  %
  % We compare our technique with a variety of off-the-shelf classifiers
  % and find that our top-ranked blame assignments have an accuracy of
  % 72\%, compared to a state-of-the-art 56\%.
  % For how many ill-typed programs can we accurately predict the source
  % of the error?
\item \textbf{Feature Utility}
  %
  Which program \emph{features are required}
  to localize errors?
   (\autoref{sec:feature-utility})
  % How much do the features described in \autoref{sec:features}
  % contribute to our predictions?
\item \textbf{Interpretability}
  %
  %% Do the models learned by \toolname
  %% correspond to our intuition about
  %% the real causes of errors?
  Are the models \emph{interpretable} using
  our intuition about type errors?
  (\autoref{sec:qualitative})

\item \textbf{Blame Utility}
  Do \toolname's blame assignments help
  users diagnose type errors?
  (\autoref{sec:user-study})
\end{itemize}
%
%\mypara{Summary of Results}
%
In the sequel we present our experimental
methodology \autoref{sec:methodology} and
then drill into how we evaluated each of
the questions above.
%
However, for the impatient reader, we begin
with a quick summary of our main results:
%
%
%\begin{itemize}
%
%\item \textbf

@@

\mypara{Blame Utility}
Finally, to test the explanatory power of our blame assigments, we
ran a user study at the University of Virginia (UVA IRB \#2014009900).
%
We included three problems in an exam in the Spring 2017 session of UVA's
undergraduate Programming Languages course (CS 4501).
%
We presented the 31 students in the course with ill-typed \ocaml\
programs and asked them to
%
(1) \emph{explain} the type error, and
%
(2) \emph{fix} the type error.
%
For each problem the student was given the ill-typed program and
either \sherrloc or \toolname's blame assignment, with no error message.

\input{threats}
\input{evaluation-accuracy}
\input{evaluation-utility}
\input{qualitative}
\input{evaluation-user-study}
